Transfer Learning in Multimodal Compositional and Relational Reasoning

### 2019-11-15 cvpr_submission/experiments.tex
Enhanced CLEVR barcharts images.
Experiments

\subsubsection{COG}
\label{sec:reasoning-cog}
For the COG dataset, the number of task groups (23) is large, so we designed a 2-level hierarchy of the task groups motivated by the
description of these tasks.

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.5\textwidth]{img/results/samnet_cog_overall_transfer.png}
	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
	\label{fig:samnet_cog_overall_transfer}
\end{figure}

\subsection{Feature transfer on CLEVR-CoGenT}
\label{sec:feature}
\begin{table}[ht]
	\label{tab:cogent_conditions}
	\centering
	\begin{adjustbox}{width=0.45\textwidth}
		\begin{tabular}{cccc}
			\toprule
			Dataset	& Cubes	& Cylinders &	Spheres	\\
			\midrule
			CoGenT A & Gray / Blue / Brown / Yellow  & Red / Green / Purple / Cyan	&	Any color  \\
			CoGenT B	&	Red / Green / Purple / Cyan &	Gray / Blue / Brown / Yellow	&	Any color \\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
\end{table}

>>>>

\subsubsection{COG}
\label{sec:reasoning-cog}
Since the number of task classes (=23) in the COG dataset is large, we designed a 2-level hierarchy of task groups using the
description of these tasks, as shown in~\cref{fig:task-groups}.

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{img/architecture/hierarchy}
	\caption{Hierarchy of Task Groups}
	\label{fig:task-groups}
\end{figure}

\bigskip

For the groups at the lowest level, we chose the following task classes to be placed in those groups:
\begin{description}
	\item[Basic:] \textit{ExistShape}, \textit{GetShape},
\textit{GetColor}, \textit{ExistColor}, \textit{Exist}
	\item[Compare Obj-Attr:] \emph{SimpleCompareColor}, \textit{SimpleCompareShape}, \textit{AndSimpleCompareShape}, 
	\textit{AndSimpleCompareColor};
	\item[Compare 2 Obj:] \textit{CompareColor}, \textit{CompareShape},  \textit{AndCompareColor}, \textit{AndCompareShape}, 
	\textit{ExistColorOf}, \textit{ExistShapeOf};
	\item[Spatial:] \textit{ExistSpace}, \textit{ExistColorSpace}, \textit{ExistShapeSpace}, \textit{GetColorSpace}, \textit{GetShapeSpace};
	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor}, \textit{ExistLastObjectSameObjectdescription}
\end{description}

We then conducted the following experiments using the Canonical variant of the COG dataset, to study 
whether transfer learning was effective in leveraging information gained by training a group at a higher level
of the hierarchy to learning the constituent task groups below that group at the leaf level.
 \begin{itemize}
	\item Train and test SAMNet on a single task group $t$ for the 5 groups at the lowest level of the hierarchy. 
	These 5 experiments fit into the traditional ML setup of single-task learning;
	\item Train on \textbf{Group A} and test separately on \textbf{Basic}, \textbf{Compare Obj-Attr} and \textbf{Compare 2 Obj};
	\item Train on \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
	can be viewed as training on \textbf{All} and testing on each group at the lowest level separately.
\end{itemize}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{img/results/samnet_cog_overall_transfer.png}
	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
	\label{fig:samnet_cog_overall_transfer}
\end{figure}

\subsection{Feature transfer on CLEVR-CoGenT}
\label{sec:feature}
\begin{table}[ht]
	\centering
	\begin{adjustbox}{width=0.45\textwidth}
		\begin{tabular}{cccc}
			\toprule
			Dataset	& Cubes	& Cylinders &	Spheres	\\
			\midrule
			CoGenT A & Gray / Blue / Brown / Yellow  & Red / Green / Purple / Cyan	&	Any color  \\
			CoGenT B	&	Red / Green / Purple / Cyan &	Gray / Blue / Brown / Yellow	&	Any color \\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
	\label{tab:cogent_conditions}
\end{table}
